### 2014-02-27 paper/concrete.tex
Done converting.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{definition}[Inclusion of information-flow control languages]
    A language \con{|(C, V, .->, erasef l)|} is included in another
    language \abs{|(C, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
    |(ap f cc) alequiv (ap f cc')|),
    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
    functorial over |.=>| (if
    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
\end{definition}

\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
    If a language \con{L} is included in a language \abs{L}, and \abs{L}
    satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \con{L} to \abs{L}, applying TINI and transporting the resulting
    equivalence back using bijectivity of $f$ over $l$-equivalences.
\end{proof}

Now we strengthen the condition to show TSNI:

\begin{definition}[Isomorphism of information-flow control languages]
    A language \con{|(C, .->, erasef l)|} is
    isomorphic to a language \abs{|iC, .->, erasef l|} are isomorphic if there exist total functions
    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and |f| and |finv| are
    functorial over both $l$-equivalences (if |cc clequiv
    cc'| then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration and multi-step derivation back.
\end{proof}
%}

>>>>

\begin{definition}[Weak isomorphism of information-flow control languages]
    A language \con{|(C, .->, erasef l)|} is weakly isomorphic to a
    language \abs{|(iC, .->, erasef l)|} if there exist total functions
    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
    |finv .. f = idf iC|.  Furthermore, the following coherence conditions
    must hold:
    \begin{itemize}
        \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
            $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
            $l$-equivalences and |.->|, and
        \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
    \end{itemize}
\end{definition}

\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
    If a language \con{L} is included in a language \abs{L}, and \abs{L}
    satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \con{L} to \abs{L}, applying TINI and transporting the resulting
    equivalence back using functoriality of |finv| over $l$-equivalences.
\end{proof}

Isomorphism requires that |finv| is functorial over reduction relations
as well, i.e. that we can extract a concrete reduction sequence from an abstract one.

\begin{definition}[Isomorphism of information-flow control languages]
    A language \con{|(C, .->, erasef l)|} is
    isomorphic to a language \abs{|(iC, .->, erasef l)|} if there exist total functions
    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and both |f| and |finv| are
    functorial over both $l$-equivalences and |.->|.
%(if |cc clequiv
%   cc'| then
%   |(ap f cc) alequiv (ap f cc')| and if |ac alequiv ac'|
%   then |(ap finv ac) clequiv (ap finv ac')|) and
%   |.->| (if
%   |cc creduce cc'| then |(ap f cc) areduce (ap f cc')| and
%   if |ac areduce ac'| then |(ap finv ac) creduce (ap finv ac')|)
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}
%}
